%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{fontspec}

\name{Chenyu LU} % Your name
%\address{15 Bis Rue Amélie \\ 75007, Paris, France} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{+33~6~50~78~29~43 \\ luchenyuxx@gmail.com} % Your phone number and email
\address{LinkedIn: https://fr.linkedin.com/in/luchenyu}
\begin{document}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experiences}

\begin{rSubsection}{Density Technologies\footnote{Density Technologies développe des logiciels métiers dédiés aux professionnels de la gestion d’actifs. Son progiciel NX Density se base sur Java.}}{Sep 2014 - en cours}{Ingénieur Informatique R\&D}{Paris, France}
\item Moved application build tool from Ant to SBT to support Scala language. Improved company's development environment by developing a Eclipse SBT plugin and evolving the continuous integration tool (Hudson). Greatly reduced the compilation time of the product.
\item Migrated product's interface layout data from XML storage to database storage, added lazy loading feature, which halfs the launching time of the product and reduces memory consumption by 100M+.
\item Developed new loading mechanism from database using queryable text data type (JSON in PostgreSQL, XML in SQLServer) and Scala macros, which resolved a blocking performance issue for a client.
\item Integrated the framework with an internationalization library (gettext). Allowing the application to have Chinese and French version and easily have more.
\end{rSubsection}

\begin{rSubsection}{Density Technologies}{Mar-Sep 2014}{Stagiaire Informatique}{Paris, France}
\item Developed a prototype of web interface for company's desktop product. Using the technics of Java, SQL, JSON, Play Framework, Scala, JavaScript, jQuery, Spray, Akka.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
 
\begin{rSection}{Formations}

{\bf Conservatoire National des Arts et Métiers, Paris} \hfill {2013-2014} \\ 
Master international de sciences et technologies, spécialité architecture et intégration des systèmes et du logiciel\\
Graduation project: ``Migration of a large desktop application to a web Interface''\\
Mark of defense: 17/20 with comment ``very good!''\medskip\\
{\bf l’Université du Sud-Est, Nanjing, Chine} \hfill {2008-2012}\\
Licence technologies de l’information et de la communication.
GPA: 4.0

\end{rSection}

% ----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Competences}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Langages de programmation & Scala, Java, Haskell, SQL, JavaScript \\
Protocoles \& APIs & PlayFromework, Akka, XML, JSON, REST \\
Bases de données & MySQL, PostgreSQL, SQLServer, H2 \\
Outils & Git, SBT, SVN, Hudson, Eclipse, IntelliJIDEA \\
Langues & Anglais: Professional Working Proficiency \\
        & Français: Limited Working Proficiency \\
        & Chinois: Native Proficiency 
\end{tabular}

\end{rSection}

% --------------------------------------------------------------------------------
% AWARDS
% -------------------------------------------------------------------------------------

\begin{rSection}{Prix}

{\bf Vainqueur du mérite de la concurrence interdisciplinaire en modélisation} \hfill {Mar-2011}\\
Issuer: The Consortium for Mathematics and Its Applications, USA
  
\end{rSection}

\end{document}
B